---
title: "Chapter 15 Instructor Demo"
author: "Thomas Lackey"
date: "2023-11-06"
output:
    html_document: default
    toc: true
    toc_float: true
    theme: spacelab
---

##### What follows is the syntax to add chunks of code to your Markdown document
##### Showing how to insert a heading and a text paragraph. 
##### Explaining How to Insert One or More Paragraphs of Text
      
      Adding paragraphs works just like any text editor. You just press enter twice and a new paragraph starts. 
      
      To start the second paragraph press enter twice and type the second paragraph.

##### What follows is the syntax to add chunks of code to your Markdown document
##### Code Chunks

Code chunks are embedded in a markdown file so that plots can be rendered, or other R commands can be executed when the markdown file is shared. 
A code chunk’s start is defined in a .Rmd file by 3 back ticks and the letter R within curly braces. The chunk is ended by three back ticks. 

You have the option to 

#### 1) print the code as well as the code's output. 
```{r}
print("some r code would go here")
```
#### 2) print just the output by passing an echo=FALSE argument 

```{r echo = FALSE}
print("some r code would go here, but you won't see the print command")
```

#### 3) see only the code, and not the output
```{r results=FALSE, message=FALSE, warning=FALSE}
print("some r code would go here, but you won't see output, you would only see the print command, you can also choose to surpress messages and warnings")
```

The easiest way to start a code chunk in an .Rmd file is to use the menu Code->Insert Chunk


##### Run a chunk of code within an .Rmd file

In an R script you typically run one command at a time. 
In an .Rmd file you may execute and entire chunk of code, to ensure that it’s working before sharing with others. 
There are several additions to the Run options when you are working with an .Rmd file. These are accessible in the drop-down menu next to the green Run arrow at the top of the Source window in R Studio. 


1. You can run the current chunk of code.


2. You can run all chunks of code that occur before the current chunk.


3. You can run a setup chunk of code. (More about this later). 

The following is an example of a chunk of code that plots the Scatter plot for the irises data that we have worked with before. In this case I have opted to show the code, as well as any messages or warnings. By testing the code chunk right here we don't have to knit the entire file! 

```{r}
library("tidyverse")
library("datasets")
ggplot(iris, 
       aes(x = Sepal.Length, y = Sepal.Width, color = Species))+
  geom_point()
```

##### formatting text in a markdown file


In this paragraph we will delineate some text as code by inserting a backtick don't forget to load    `library("datasets")`

Use the ^ and the ~ to provide a superscript^2^ or a subscript~2~ to text.

Use dashes to make unordered lists of items
- unordered item 1
- unordered item 2
  - unordered sub item for item 2

Use an asterik to make some text *italic*, or two asterisk to make some text **bold**

##### Creating Dynamic Code
